---
title: "case_study"
author: "Paula Wu"
date: "10/14/2021"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(ggridges)

# set global variable
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
      
```

```{r}
library(p8105.datasets)
data(nyc_airbnb)
```

* is price correlated with review score?
* which neighborhood is most popular? most expensive?
* which neighborhood has the highest reviews?
* is availability related to price?
* is room type related to neighborhood?
* is length of stay related to neighborhood group (borough)?
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location/2) %>% 
  rename(borough = neighbourhood_group)
view(nyc_airbnb)
```

Let's try to count things:
```{r}
nyc_airbnb %>% 
  count(borough, room_type) #janitor::tabyl(borough, room_type)
```
```{r}
study_data = 
  nyc_airbnb %>% 
  select(-c(id, host_id, host_name, lat, long))
view(study_data)
```

Mine: minimum nights related to review_per_month? or stars?
```{r}
study_data = 
  study_data %>% 
  mutate(review_range = round(reviews_per_month, 0))
  #group_by(minimum_nights, reviews_per_month) %>% 
  #summarize(n_obs = n())
```
```{r}
study_data %>% 
  count(minimum_nights, review_range)
  #pivot_wider()
```
Let's look at price and room type
```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  facet_grid(.~room_type)
```
Price and neighborhood
```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(desc(mean_price))

nyc_airbnb %>% 
  filter(borough == "Manhattan",
         price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% # order by the median 
  ggplot(aes(x = neighbourhood, y = price))+
  geom_boxplot() + 
  coord_flip() + # flip coordinates
  facet_grid(.~room_type)  # not a lot of shared room in expensive neighborhood
```
```{r}

```



